---
title: "scanMiRData"
author: 
- name: Pierre-Luc Germain
  affiliation:
    - D-HEST Institute for Neuroscience, ETH
    - Lab of Statistical Bioinformatics, UZH
- name: Michael Soutschek
  affiliation: Lab of Systems Neuroscience, D-HEST Institute for Neuroscience, ETH
- name: Fridolin Groß
  affiliation: Lab of Systems Neuroscience, D-HEST Institute for Neuroscience, ETH
package: scanMiR
output:
  BiocStyle::html_document
abstract: |
  Introduction to scanMiRData
vignette: |
  %\VignetteIndexEntry{scanMiRData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
library(BiocStyle)
```

The `scanMiRData` package contains `KdModel` collections corresponding to all human, mouse and rat [mirbase](http:/mirbase.org/) miRNAs. These represent the miRNA binding affinities (or more exactly, dissociation rates) predicted using the CNN from [McGeary, Lin et al. (2019)](https://dx.doi.org/10.1126/science.aav1741). To know more about the `KdModel` and `KdModelList` classes, see the corresponding vignette in the `scanMiR` package.

# Loading the collections

The objects can be loaded to the environment using `data`:

```{r}
library(scanMiR)
data("mmu", package="scanMiRData")
summary(mmu)
head(mmu)
```

Alternatively, they can also be loaded (and filtered) through a convenient function:

```{r}
library(scanMiRData)
mmu <- getKdModels("mmu", categories=c("Conserved across vertebrates", 
                                       "Conserved across mammals"))
summary(mmu)
```
Summary of the other two collections:

```{r}
summary(getKdModels("hsa"))
summary(getKdModels("rno"))
```

<br/><br/>

# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
